### 2019-09-13 README.Rmd
testing escape in tables

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  eval.after = 'fig.cap'
) 
options(knitr.table.format = "html")
```
# diffEnrich

@@

```{r get_kegg_kable, warning=FALSE, echo=FALSE, message=FALSE}
if (require(kableExtra)){
knitr::kable(kegg_df,
             caption = "Table 1. Description of data sets generated from accessing KEGG REST API", row.names = FALSE) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = T)
}
```

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  eval.after = 'fig.cap'
) 
```
# diffEnrich

@@

```{r get_kegg_kable, warning=FALSE, echo=FALSE, message=FALSE}
if (require(kableExtra)){
knitr::kable(kegg_df, format = 'html',escape = FALSE,
             caption = "Table 1. Description of data sets generated from accessing KEGG REST API", row.names = FALSE) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = T)
}
```
